Hypertension and microbiome

### 2019-01-25 articletwo.Rmd
Minor

```{r alphabeta definitions}
dset.alpha <- meta.merge.alphadiversity(pseq.species)
alphaglm <- calculateglm(dset.alpha, modelstring = "%s ~ BL_AGE + SEX + BMI + CURR_SMOKE + Q57X + DIAB + BL_USE_RX_C03 + BL_USE_RX_C07 + BL_USE_RX_C08 + BL_USE_RX_C09  + diversities_shannon")
alpha.diversity <- alphaglm %>% select(response, estimate, p.value)

adonis.species  <- readRDS("rds/adonis.species.rds")
adonis.species$min

beta.diversity <- adonis.species %>%
    data.table::rbindlist(id = "model_name") %>%
    dplyr::filter(term %in% c("MAP", "SYSTM", "DIASM", "PULSEPRESSURE", "HYPERTENSION")) %>%
    dplyr::select(response, R2)

diversity <- merge(alpha.diversity, beta.diversity, by = "response") %>%
    merge(names.dset %>% select(Covariate, Category, Name), by.x ="response", by.y = "Covariate") %>%
    mutate(Qstar = ifelse(p.value < 0.05, '*', ' '))
```

```{r save grob}
alpha.diversity <- plot.alpha(diversity)
beta.diversity <- plot.beta(diversity)
gs4 <- list(alpha.diversity$yaxis,
            alpha.diversity$plot,
            beta.diversity$plot,  
            alpha.diversity$legend,
            alpha.diversity$xaxis,
            beta.diversity$xaxis,
            plot.xlab.beta.diversity,
            text_grob("A", vjust = "top", hjust= "left", size = 20))

g4 <- arrangeGrob(grobs = gs4,
                  layout_matrix = rbind(
                      c(8,    NA,    NA,    NA, NA, 4),
                      c(NA, 1,    2,    3, NA, 4),
                      c(NA, 1,    2,    3, NA, NA),
                      c(NA, NA, 5,    6, NA, NA),
                      c(NA, NA, NA, 7, NA, NA)),
                  widths=c(0.7, 4, 0.7, 5, 0.7, 4),
                  heights=c(1, 1, 6, 1, 2))
ggsave(file = "cache/alpha-beta.png", plot=g4, height=3, width=9)

@@

@@

ggsave(file = "cache/pca.png", plot = pcaplot, height = 5, width = 9, dpi = 300)

writeimage(doc, 2, "cache/pca.png", "Alpha-beta", "footer", width = 7)
```

>>>>

```{r alphabeta definitions}
dset.alpha <- meta.merge.alphadiversity(pseq.species)
alphadiversity <- list(
    min = calculateglm(dset.alpha, modelstring = "%s ~ BL_AGE + SEX  + diversities_shannon"),
    max = calculateglm(dset.alpha, modelstring = "%s ~ BL_AGE + SEX + BMI + CURR_SMOKE + Q57X + DIAB + BL_USE_RX_C03 + BL_USE_RX_C07 + BL_USE_RX_C08 + BL_USE_RX_C09  + diversities_shannon"))
betadiversity  <- readRDS("rds/adonis.species.rds")
diversities <- mergediversities(alphadiversity, betadiversity)

betadiversity$min$model_1 %>% select(term, R2)
betadiversity$max$model_1 %>% select(term, R2)

@@

Max values for alpha diversity `r diversities$max %>% pull(estimate)
								  %>% abs %>% max %>% round(., 2)` and
								  `r diversities$mmin %>%
								  pull(estimate) %>% abs %>% max %>%
								  round(., 2)`.

```{r save grob}
alpha.diversity.min <- plot.alpha(diversities$min, colorlimit = 1.3)
alpha.diversity.max <- plot.alpha(diversities$max, colorlimit = 1.3)
beta.diversity.min <- plot.beta(diversities$min)
beta.diversity.max <- plot.beta(diversities$max)

gs4 <- list(alpha.diversity.min$yaxis,
            alpha.diversity.min$plot,
            beta.diversity.min$plot,  
            alpha.diversity.min$legend,
            alpha.diversity.min$xaxis,
            beta.diversity.min$xaxis,
            beta.diversity.min$xlab,
            text_grob("A.", size = 18),
            alpha.diversity.max$yaxis,
            alpha.diversity.max$plot,
            beta.diversity.max$plot,  
            alpha.diversity.max$xaxis,
            beta.diversity.max$xaxis,
            beta.diversity.max$xlab,
            text_grob("B.", size = 18))

g4 <- arrangeGrob(grobs = gs4,
                  layout_matrix = rbind(
                      c(8,    NA,    NA, NA,   NA, NA, NA),
                      c(NA, 1,    2,    NA, 3, NA, NA),
                      c(NA, 1,    2,    NA, 3, NA, 4),
                      c(NA, NA, 5,    NA,6, NA, 4),
                      c(NA, NA, NA, NA,7, NA, 4),
                      c(15,    NA,    NA, NA,   NA, NA, 4),
                      c(NA, 9,    10,  NA,  11, NA, 4),
                      c(NA, 9,    10,  NA,  11, NA, NA),
                      c(NA, NA, 12,   NA, 13, NA, NA),
                      c(NA, NA, NA, NA,14, NA, NA)),
                  widths=c(0.7, 4, 0.7, 0.1, 5, 0.7, 4),
                  heights=rep(c(1, 1, 6, 1, 2), 2))
ggsave(file = "cache/alpha-beta.png", plot=g4, height=6, width=9)
```

```{r Write figure 2}
fig1head <- "alpha beta figure"
fig1foot <- ""
writeimage(doc, 1, "cache/alpha-beta.png", fig1head, fig1foot)
```

@@

ggsave(file = "cache/pca.png", plot = pcaplot, height = 5, width = 9, dpi = 300)
```
